Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/results.tex
pollish replication Fig s4

To be able to replicate the result of Figure S4 of the suplementary material of Ellis et al, we
need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper)  that is not a 
longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
angle of incidence runs (see Figure \ref{fig:ellis_ang_inc}). As we mentioned the longitudinal modes, due to its nature, do not appear when we 
have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
that it's not a longitudinal mode.

@@

Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence (see Figure \ref{fig:ellis_ang_inc}).

In Figure \ref{fig:AR_22_vs_norm} and Table \ref{tab:ar_peaks} we show the resonance peaks and
their corresponding wavelengths. In the table we mark in bold the peaks which correspond to 
the $E^{\parallel}_{100}$ mode.

@@

Once we identify the proper modes, we proceed to the replication of Figure S4 on the 
supplementary material of Ellis et al work. It is worth mentioning that we limit ourselves to
the replication of the black curve in their plot, since in this case the pillars are separated 
by 5000 nm which means the coupling effects are negligible. Figure \ref{fig:rep_FS4_ellis} shows
the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
the cases

@@

\subsubsection{Validation of \pygbe against Fig 2a experimental results}

>>>>

\subsubsection{Replication of Figure S4 of supplementary material of Ellis et al. 2016}

To be able to replicate the result of Figure S4 of the supplementary material of Ellis et al, we
need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper) that is not a 
longitudinal mode. The longitudinal mode appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} show the results of the extinction 
cross section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm), for normal 
and 22 degrees angle of incidence. The simulations where performed 
for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence as shown on see Figure \ref{fig:ellis_ang_inc}. From these results we select 
the lower mode that it is not a longitudinal one and extract its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al (digitized using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all
the cases.

@@

@@

@@

\subsubsection{Validation of \pygbe against Fig 2a experimental results, and replication of corresponfding computations}
